Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Add some placeholders to Section 2, small improvements

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 30)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$ and
$z_{\text{max}}=425\,\pc$. The orbit is plotted in \Gus{Appendix x}. We then
suppose that an observer makes observations of this orbit in a coordinate
system that is incorrect in radius by $200\,\pc$ and height by $100\,\pc$ ---
we subtract the vector $(200, 0, 100)\,\pc$ from each position in the orbit.
This corresponds to an observer physically located at the position $(8, 0,
0)\,\kpc$ but erroneously thinking they are located at $(8.2, 0, 0.1)\,\kpc$.

Using the observations of the orbit that this erroneous observer makes every
$\Myr$\footnote{In addition to being erroneous, we also assume our fictitious
observer is immortal.}, we perform the same orbit integration procedure as
before to compute the actions our observer would make in the incorrect
coordinate system over the duration of the orbit. The erroneous computed
actions are shown for the first $\Gyr$ of the orbit in
Figure~\ref{fig:one_orbit_wrong_ref}. Occasionally the numerical scheme fails
and very large actions are reported by \texttt{gala}
--- we perform a $5\sigma$ clip on each action to exclude such orbits, but
this only excludes a total of $5$ orbits out of the $1000$ considered for
Figure~\ref{fig:one_orbit_wrong_ref}. Some numerical artifacts remain, but the
vast majority of orbits are computed properly.

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. The
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2 \actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\%$ and $85.7\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ does not depend on the value of $z$. It is
worth pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=425\,\pc$ --- a $24\%$ error --- induced an $85.7\%$ error in
the computation of $J_z$.

>>>>

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 30)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$ and
$z_{\text{max}}=425\,\pc$. The orbit is plotted in \Gus{Appendix x}. We then
suppose that an observer makes observations of this orbit in a coordinate
system that is incorrect in height by $100\,\pc$ --- i.e. we subtract the
vector $(0, 0, 100)\,\pc$ from each position in the orbit. This corresponds to
an observer physically located at the position $(8, 0, 0)\,\kpc$ but
erroneously thinking they are located at $(8, 0, 0.1)\,\kpc$.

Using the observations of the orbit that this erroneous (and immortal)
observer makes every $\Myr$, we perform the same orbit integration procedure
as before to compute the actions our observer would observe in the incorrect
coordinate system over the duration of the orbit. The erroneous computed
actions are shown for the first $\Gyr$ of the orbit in the {\em upper} panels
Figure~\ref{fig:one_orbit_wrong_ref}. Occasionally the numerical scheme fails
and very large actions are reported by \texttt{gala}
--- we perform a $5\sigma$ clip on each action to exclude such orbits, but
    this only excludes a total of $5$ orbits out of the $1000$ considered for
    Figure~\ref{fig:one_orbit_wrong_ref}. Some numerical artifacts remain, but
    the vast majority of orbits are computed properly. We perform the same
    procedure but assume a $100\,\pc$ offset in the $x$ component (i.e.
    subtracting the vector $(100, 0, 0)\,\pc$) in the {\em lower} panels. This
    is equivalent to an observer making an incorrect measurement of the Solar
    radius.

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. For an error in
$z$ ({\em upper} panels), the 95\textsuperscript{th} minus
5\textsuperscript{th} percentiles are $2.2$ and $6.2 \actunit$ for $J_r$ and
$J_z$, respectively. These are fractional errors of $5.7\%$ and $85.7\%$,
respectively. The error induced in $L_z$ is negligible, as expected since
$L_z$ does not depend on the value of $z$. It is worth pointing out that a
$100\,\pc$ error in an orbit with $z_{\text{max}}=425\,\pc$ --- a $24\%$ error
--- induced an $85.7\%$ error in the computation of $J_z$.

For an error in the $x$ component (or Solar radius), the 95\textsuperscript{th} minus
5\textsuperscript{th} percentiles are $x$, $y$, and $z \actunit$ for $J_r$, $L_z$ and
$J_z$, respectively. These are fractional errors of $x\%$, $y\%$ and $z\%$,
respectively.
